\documentclass[11pt,a4paper]{article}

% ---------------- Packages ----------------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}

% ---------------- Branding ----------------
\definecolor{Accent}{HTML}{0A7AA6}
\hypersetup{
  colorlinks=true,
  linkcolor=Accent,
  urlcolor=Accent,
  citecolor=Accent
}

\newcommand{\product}{PropVisions}

\begin{document}

\begin{center}
  {\Huge \bf Service Level Agreement (SLA)} \\[6pt]
  {\large for Beta Users of \product} \\[12pt]
  {\small Version 1.0 -- Last Updated: \today}
\end{center}

\section*{1. Introduction}
This Service Level Agreement (SLA) outlines the commitments, responsibilities, and expectations between \textbf{\product} (the ``Provider'') and beta testers, pilot users, or paying subscribers (the ``Customer'') regarding the availability, performance, and support of the \product\ platform.

The SLA is designed to provide transparency and confidence while acknowledging that the platform is in a \textbf{Beta stage}, during which improvements, changes, and occasional instability may occur.

\section*{2. Scope of Services}
The SLA covers:
\begin{itemize}[left=0pt]
  \item Web application access (demo, dashboard, exports).
  \item API services (analysis pipeline, metrics, feedback logging).
  \item Document exports (PDF, Excel).
  \item Community support (Discord server, email).
\end{itemize}

Excluded from this SLA are:
\begin{itemize}[left=0pt]
  \item Third-party dependencies (e.g. property portals, external APIs, payment providers).
  \item User devices, internet connections, or environments outside Provider’s control.
  \item Force majeure events (natural disasters, global outages, war, government restrictions).
\end{itemize}

\section*{3. Service Availability}
\begin{longtable}{@{}p{0.25\linewidth}p{0.70\linewidth}@{}}
\toprule
\textbf{Service} & \textbf{Target Availability (Beta)} \\
\midrule
Web application uptime & 95\% monthly average \\
API uptime & 95\% monthly average \\
PDF/Excel export generation & 90\% monthly average \\
Discord support & Available 7 days/week, monitored daily \\
Email support & 1--2 business days response time \\
\bottomrule
\end{longtable}

\section*{4. Support and Response Times}
Issues are triaged into severity levels:

\begin{longtable}{@{}p{0.20\linewidth}p{0.30\linewidth}p{0.40\linewidth}@{}}
\toprule
\textbf{Severity} & \textbf{Definition} & \textbf{Target Response} \\
\midrule
Critical (P1) & Service completely unavailable or critical business impact. & Acknowledgement within 4 hrs, workaround within 24 hrs. \\
High (P2) & Major functionality impaired, but workarounds exist. & Acknowledgement within 8 hrs, resolution within 3 days. \\
Medium (P3) & Minor issues, non-critical bugs, limited impact. & Acknowledgement within 2 business days, resolution within roadmap cycle. \\
Low (P4) & Cosmetic issues, feature requests, documentation queries. & Added to backlog, prioritised in product roadmap. \\
\bottomrule
\end{longtable}

\section*{5. Maintenance and Updates}
\begin{itemize}[left=0pt]
  \item Planned maintenance will be communicated at least \textbf{48 hours} in advance via Discord and email.
  \item Emergency maintenance (e.g. security patches) may occur without notice but will be announced retrospectively.
  \item Feature updates may be released weekly as part of Beta iteration.
\end{itemize}

\section*{6. Data Handling and Security}
\begin{itemize}[left=0pt]
  \item \product\ aligns with GDPR principles: minimal personal data collection, explicit consent, and clear deletion policies.
  \item Customer data is processed only for the purposes of providing analysis and exports.
  \item Data storage: secure, encrypted at rest and in transit.
  \item Users may request deletion of their data at any time via email or support channel.
\end{itemize}

\section*{7. Customer Responsibilities}
\begin{itemize}[left=0pt]
  \item Provide accurate information when submitting properties for analysis.
  \item Ensure that submitted URLs are legally accessible and do not infringe third-party rights.
  \item Respect community guidelines in Discord (no abuse, spam, or disclosure of sensitive personal data).
  \item Accept that outputs are estimates and not investment advice.
\end{itemize}

\section*{8. Limitations of Liability}
\begin{itemize}[left=0pt]
  \item \product\ provides outputs ``as is'' during Beta; accuracy is not guaranteed.
  \item The Provider is not liable for financial loss, investment outcomes, or indirect damages arising from use of the platform.
  \item Maximum liability is limited to the total fees paid by the Customer during the last three months.
\end{itemize}

\section*{9. SLA Credits (Beta Phase)}
\begin{itemize}[left=0pt]
  \item As this is a Beta programme, \textbf{no monetary credits} are issued for downtime or SLA breaches.
  \item Instead, users may receive extended access, free usage credits, or early access to premium features.
\end{itemize}

\section*{10. Review and Updates}
\begin{itemize}[left=0pt]
  \item This SLA is reviewed every 90 days during Beta.
  \item Updates are communicated in writing via Discord and email.
  \item Continued use of the service constitutes acceptance of updated terms.
\end{itemize}

\section*{11. Acceptance}
By using the \product\ platform, the Customer acknowledges that they have read, understood, and agree to the terms of this SLA.

\vspace{1cm}
\noindent \textbf{For and on behalf of \product} \\[12pt]

Signature: \rule{6cm}{0.4pt} \\
Name: \rule{6cm}{0.4pt} \\
Role: \rule{6cm}{0.4pt} \\
Date: \rule{6cm}{0.4pt} \\

\end{document}
