\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{booktabs}

\definecolor{Accent}{HTML}{0A7AA6}
\hypersetup{
  colorlinks=true,
  linkcolor=Accent,
  urlcolor=Accent
}

\newcommand{\product}{PropVisions}

\begin{document}

\begin{center}
  {\Huge \bfseries \product Beta Programme}\\[4pt]
  {\large 10 Seats Only – Honest Early Access}
\end{center}

\section*{What is \product?}
An AI tool that turns any property listing into an investor-ready report:
\begin{itemize}[leftmargin=*]
  \item Refurbishment cost estimates from photos.
  \item Rent, yield, ROI and cash flow forecasts.
  \item Exportable PDFs for clients or partners.
\end{itemize}

\section*{Why Beta?}
This is an early build. Today, refurb can be close (e.g.\ £20k vs £22k) but also off (£11k vs £22k). Rent is based on comps but still refining. Larger photo sets may take minutes.  
Beta users supply feedback (actual refurb/rent) so accuracy converges quickly.

\section*{Your Role}
\begin{itemize}[leftmargin=*]
  \item Run your own or on-market deals through the tool.
  \item Share quick feedback: actual refurb cost and rent.
  \item Help shape ``Low / Mid / High'' refurb bands.
  \item Optionally: test custom integrations (CRM, API, workflows).
\end{itemize}

\section*{What You Get}
\begin{itemize}[leftmargin=*]
  \item Early access before public launch.
  \item Priority influence on features and accuracy.
  \item Reduced lifetime pricing locked in.
  \item First option on custom setups.
\end{itemize}

\section*{Key Details}
\begin{tabular}{@{}ll}
\toprule
Seats & 10 only (first come) \\
Start & \textasciitilde 1 month from now \\
Duration & 3 months initial, rolling thereafter \\
Pricing & Discounted beta rate; locked lifetime \\
\bottomrule
\end{tabular}

\vspace{1em}
\noindent \textbf{Transparency:} \product\ is not perfect yet. Accuracy improves as real data flows in. Your input directly trains the system. In return, you secure insider access to what can become the go-to property analysis platform.

\vfill
\begin{center}
  \textbf{Reserve your slot:} \href{https://www.propvisions.com/}{propvisions.com} \\
  (10 seats only; several already reserved)
\end{center}

\end{document}
