\documentclass[11pt,a4paper]{article}

% ---------------- Packages ----------------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{booktabs}

% ---------------- Branding ----------------
\definecolor{Accent}{HTML}{0A7AA6}
\hypersetup{
  colorlinks=true,
  linkcolor=Accent,
  urlcolor=Accent,
  citecolor=Accent
}

\newcommand{\product}{PropertyScout}
\newcommand{\tagline}{AI Deal Analysis \& Alerts for Property Investors and Agents}

% ---------------- Title ----------------
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  {\LARGE\bfseries\color{Accent}\product\par}
  \vspace{0.25em}
  {\large \tagline\par}
  \vspace{0.5em}
  {\normalsize \textbf{Beta Client Brief} \textbar\  \today\par}
  \vspace{0.75em}
  \hrule height 1pt \vspace{0.8em}
}
\makeatother

% ---------------- Lists ----------------
\setlist[itemize]{nosep,left=0pt,label=\textbullet}
\setlist[enumerate]{nosep,left=0pt}

\begin{document}
\title{\product}
\author{}
\date{}
\maketitle

\section*{One line}
\textbf{\product} turns a property listing URL \emph{or} API query into a full investment snapshot---refurb costs, rent band (using historical rent data), yield, ROI, EPC and comparables---and alerts you to new or returning deals. It is in \textbf{active beta}: fast progress, imperfect outputs.

\section*{Beta status \& what to expect (read first)}
\textbf{This is a working beta.} We are prioritising speed and learning:
\begin{itemize}
  \item Results will \textbf{not} be perfect yet; UI is functional rather than pretty.
  \item Current accuracy is \textbf{variable} by area and listing quality; we will publish baselines after initial pilots.
  \item Our target is \textbf{$\geq$\,80\%} accuracy across core outputs (rent band selection, refurb banding, EPC matching) as we iterate.
  \item A simple, transparent model lets you adjust assumptions (management\%, voids, fees) and see the effect immediately.
  \item Human judgement remains important; we provide confidence bands and clear levers to tweak.
\end{itemize}

\section*{What works today (MVP)}
\begin{itemize}
  \item \textbf{Paste a URL} (portals or agent sites) $\rightarrow$ clean scrape $\rightarrow$ structured fields (price, layout, images, agent, postcode).
  \item \textbf{Refurb from photos:} Per-room line items using regional baseline rates; editable totals.
  \item \textbf{Rent estimate:} Combines \emph{historical rent data}, postcode features and listing signals to produce monthly/annual \emph{rent bands} with a confidence indicator.
  \item \textbf{Investment metrics:} Stamp duty, fees, management\%, voids, maintenance $\rightarrow$ yield, cash flow, ROI.
  \item \textbf{EPC enrichment:} Rating and measures where available; full record stored for reporting.
  \item \textbf{Comps checks (basic):} Recent local sales/rental comps to flag \pounds/sq\,ft outliers.
  \item \textbf{Exports \& alerts:} Auto PDF/Excel; Slack/email notifications on completion.
\end{itemize}

\section*{Launch (v1) Unified Search \& API Integrations}
\textbf{Ready at go-live.} Beyond single URLs, \product{} will ship with a unified search bar and configurable API connectors:
\begin{itemize}
  \item \textbf{Unified search bar:} Search by postcode/filters \emph{or} paste any listing URL.
  \item \textbf{Prebuilt connectors:} Rightmove, Zoopla, OnTheMarket, major auction platforms, and selected agent feeds (where APIs or data partnerships are available).
  \item \textbf{Area coverage:} Works across all regions where APIs/feeds exist; falls back to one-time URL ingest for other sites.
  \item \textbf{One-time URL ingest:} Run ad-hoc analyses for \emph{any} agent/auction page (HTML cleaned to structured JSON).
  \item \textbf{Per-client customisation:} Enable/disable sources, set query defaults \& quotas, and prioritise data sources by reliability for your patch.
  \item \textbf{De-duplication \& canonicals:} Merge the same listing across sources; canonicalise by address+agent+photos.
  \item \textbf{Scheduling \& batch import:} Saved searches with periodic runs; daily digests of new/returning/price-dropped deals.
  \item \textbf{Compliance \& ops:} Honour site T\&Cs and rate limits; API credentials stored securely; full audit logs \& error handling.
\end{itemize}

\section*{How it makes estimates (transparent methods)}
\begin{itemize}
  \item \textbf{Historical rent data:} Local historic rents and listing features (beds, type, postcode) to place the property into a realistic rent band; your edits re-calibrate per area.
  \item \textbf{Refurb:} Image classification (room type), baseline regional trade rates, itemised scope; override any line item; add contingencies.
  \item \textbf{Sanity checks:} Simple comparables, EPC cross-refs, and outlier flags to nudge manual review when needed.
  \item \textbf{Data hygiene:} De-dup by URL/address; validation on key numeric fields; error logs and retries.
\end{itemize}

\section*{Mortgage module: now and next}
\textbf{Today}
\begin{itemize}
  \item Standard mortgage assumptions (rates, LTV, fees) included in ROI/yield and cash-flow calculations.
\end{itemize}
\textbf{Coming}
\begin{itemize}
  \item \textbf{Mortgage types:} IO vs.\ repayment, BTL vs.\ residential, product fees, ERC modelling.
  \item \textbf{Rate changes \& forward rates:} Integrate live rate updates and forward curves to explore re-mortgage timing windows.
  \item \textbf{Live dashboard (Q3):} Visualise projected payments, DSCR/ICR under different rate paths; export scenarios.
\end{itemize}

\section*{Deal discovery (Q2 focus)}
\begin{itemize}
  \item \textbf{Off-Market Sourcing Module:} Agent coverage lists \& cadence; GDPR-compliant outreach templates; probate/distress signals where available; lightweight CRM for follow-ups.
  \item \textbf{Deal-status change watcher:} Monitors portals for \emph{newly listed}, \emph{price drops}, \emph{back on market/fall-through} and \emph{time-on-market} thresholds; smart filters by postcode/price/bed/yield/refurb budget; alerts with a pre-built analysis.
\end{itemize}

\section*{Accuracy plan \& measurement}
We measure and publish decision-focused metrics:
\begin{center}
\begin{tabularx}{\linewidth}{@{}p{3.2cm} X X@{}}
\toprule
\textbf{Output} & \textbf{Metric} & \textbf{Target (beta $\rightarrow$ stable)}\\
\midrule
Rent band & Mean absolute \% error (MAPE) on achieved rent; band hit-rate & \textasciitilde 20--25\% $\rightarrow$ \textbf{$\leq$ 15\%}, band hit-rate $\geq$ \textbf{80\%}\\
Refurb total & MAPE vs.\ final invoices/quotes & \textasciitilde 25--35\% $\rightarrow$ \textbf{$\leq$ 20\%}\\
EPC match & Correct record match rate & \textasciitilde 85\% $\rightarrow$ \textbf{$\geq$ 95\%}\\
Yield/ROI & Propagated error from inputs & Confidence bands shown; narrows as inputs confirmed\\
\bottomrule
\end{tabularx}
\end{center}

\noindent\textbf{Improvement loop}
\begin{itemize}
  \item \textbf{Feedback-at-source:} Users nudge rent/refurb bands; we log adjustments for retraining.
  \item \textbf{Area priors:} Store per-postcode priors (rent per bed, refurb per m$^2$ by room type).
  \item \textbf{Model updates:} Weekly prompt/model tweaks during beta; monthly calibration once stable.
\end{itemize}

\section*{Roadmap (high level)}
\begin{center}
\begin{tabularx}{\linewidth}{@{}p{2.2cm} X X@{}}
\toprule
\textbf{When} & \textbf{Highlights} & \textbf{Accuracy focus}\\
\midrule
Now (Beta) & URL$\rightarrow$analysis, refurb from photos, rent bands (historical data), ROI/EPC, PDF/Excel, alerts & Establish baselines; expose assumptions; log user edits\\
\textbf{Launch (v1)} & \textbf{Unified search bar}, \textbf{API integrations} (Rightmove, Zoopla, \dots), one-time URLs, per-client source customisation, de-dup, batch import & Source reliability weighting; cross-source validation\\
Q2 & Off-market module, deal-status watcher, smarter comps, regional calibration & Push rent band hit-rate; reduce refurb variance\\
Q3 & Mortgage types, forward rates, \textbf{live dashboard} for scenarios; remortgage assistant & Validate DSCR/ICR under rate paths; shrink confidence bands\\
\bottomrule
\end{tabularx}
\end{center}

\section*{Risks \& mitigations}
\begin{itemize}
  \item \textbf{Data gaps/changes:} Portal HTML changes or missing fields $\rightarrow$ monitored scrapers, fast fallbacks, error alerts.
  \item \textbf{Model drift:} Market moves faster than priors $\rightarrow$ rolling calibration and user-feedback signals.
  \item \textbf{Local quirks:} Unique stock or micro-markets $\rightarrow$ per-area priors and optional client fine-tuning.
  \item \textbf{API constraints:} Rate limits/T\&Cs $\rightarrow$ queueing, caching, credential vaulting, and clear SLAs.
\end{itemize}   

\section*{How to pilot}
\begin{itemize}
  \item Share \textbf{target postcodes} and 10--20 sample links; optionally provide \textbf{portal API keys} for your sources.
  \item We configure your \textbf{source mix} (APIs + ad-hoc URLs), run a guided pilot (2--4 weeks), and deliver \textbf{analysis packs} (PDF/Excel) with alerts.
  \item No payment until you have a working pilot you can use. Beta pricing locks in a discount; optional \textbf{custom area fine-tuning} available for teams/regions.
\end{itemize}

\section*{What this is not (yet)}
\begin{itemize}
  \item A guarantee of valuation or lending terms.
  \item A replacement for surveys, quotes or legal advice.
  \item A fully polished UI---that arrives after we lock accuracy and workflows.
\end{itemize}

\section*{Call to action}
If you can tolerate ``beta rough edges'' in exchange for speed and a say in the roadmap, we would love you in the first cohort. Send postcodes, links, and any API keys; we will have you analysing deals within days.\\[0.25em]
\textit{Contact:} \href{mailto:hello@propertyscout.example}{hello@propertyscout.example} \quad\textbar\quad \href{https://propertyscout.example}{propertyscout.example}

\end{document}
